### 2020-12-16 ch02_scientific_background/scientific_background.tex
Started section on MDER

To quantify the effects of different feedbacks, a reference system with a basic
response needs to be defined, which is a crucial aspect of feedback analysis
\autocite{Roe2009}. Usually, the idealization of a blackbody Earth without an
atmosphere is used for that: In equilibrium, the incoming solar irradiance is
balanced with an outgoing thermal irradiance $J_0$ that solely depends on the
global mean surface temperature $T_0$ following the Stefan–Boltzmann law
\begin{equation}
  J_0 = -\sigma T_0^4.
  \label{eq:02:stefan_boltzmann_law_eq}
\end{equation}
$\sigma \approx 5.67 \unit{W m^{-2} K^{-4}}$ is the Stefan–Boltzmann constant.
To answer an external forcing $F$, the climate system reacts with a response
$R$ expressed by a change in the global mean surface temperature $\Delta T$:
\begin{equation}
  J_0 + R = -\sigma \left( T_0 + \Delta T \right)^4.
  \label{eq:02:stefan_boltzmann_law_non_eq}
\end{equation}
Since the temperature change caused by an anthropogenic forcing is much smaller
than the equilibrium temperature $\Delta T \ll T_0 \approx 255 \unit{K}$, a
simple first-order Taylor expansion can be used to linearize the blackbody
response:
\begin{equation}
  -\sigma \left( T_0 + \Delta T \right)^4 \approx J_0 - 4 \sigma T_0^3 \cdot
  \Delta T.
  \label{eq:02:stefan_boltzmann_law_lin}
\end{equation}
Thus, by comparing
\cref{eq:02:stefan_boltzmann_law_non_eq,eq:02:stefan_boltzmann_law_lin} the
climate response $R$ can be expressed as
\begin{equation}
  R = -4 \sigma T_0^3 \cdot \Delta T \coloneq \lambda_\text{BB} \cdot \Delta T
  \label{eq:02:linear_blackbody_response}
\end{equation}
with the blackbody feedback parameter $\lambda_\text{BB} \approx -3.8 \unit{W
  m^{-2} K^{-1}}$. Results from climate models and analyses of observations
confirm this linear relationship between $R$ and $\Delta T$
\autocite{Gregory2004}. However, the value of this linear constant $\lambda$,
the \emph{climate feedback parameter}, is found to be considerably larger than
the blackbody response ($\lambda \approx -1.0 \unit{W m^{-2} K^{-1}}$),
indicating that additional processes affect the Earth's radiative balance: the
climate feedbacks \autocite{Flato2013, Gregory2009}. Since climate models
suggest that the radiative effects of these additional feedbacks are also
proportional to $\Delta T$ \autocite{Gregory2008a},
\cref{eq:02:linear_blackbody_response} can be adjusted to
\begin{equation}
  R = \lambda \cdot \Delta T = \left( \lambda_\text{BB} + \lambda_\text{WV} +
  \lambda_\text{Albedo} + \lambda_\text{Cloud} + \ldots \right) \cdot \Delta T.
  \label{eq:02:linear_response}
\end{equation}
$\lambda_\text{WV}$ refers to the water vapor feedback, $\lambda_\text{Albedo}$
to the snow/ice albedo feedback and $\lambda_\text{Cloud}$ to the cloud
feedback. Thus, the overall climate feedback parameter $\lambda$ can be written
as the sum of the individual feedback parameters $\lambda_i$:
\begin{equation}
  \lambda = \sum_i \lambda_i.
  \label{eq:02:lambda_as_sum_of_lambdas}
\end{equation}
Positive values of $\lambda_i$ indicate positive feedbacks (\eg{} the water
vapor feedback) and negative values indicate negative feedbacks (\eg{} the
blackbody feedback). This equation assumes that the individual radiative
responses from the different feedbacks are independent, which is a reasonable
first-order approximation but not entirely true \autocite{Soden2008}.

@@

One possible mathematical framework for the evaluation of emergent constraints
is based on linear regression and Gaussian probability densities
\autocite{Cox2013, Cox2018}. Let $x_m$ be the observable predictor variable for
climate model $m$ and $y_m$ the corresponding target variable. To find the
linear emergent relationship for the climate model ensemble $\left\{ \left(
x_m, y_m \right) \right\}$, a linear regression model
\begin{equation}
  \hat{y}(x) = a + b x
  \label{eq:02:linear_regression_y}
\end{equation}
for the predicted target variable $\hat{y}$ with intercept $a$ and slope $b$ is
used. Fitting this regression line with ordinary least squares includes
minimizing the standard error $s$ of the estimate
\begin{equation}
  s^2 = \frac{1}{M - 2} \sum_{m=1}^M \left( y_m - \hat{y}_m \right)^2,
  \label{eq:02:sse}
\end{equation}
where $\hat{y}_m \coloneq \hat{y}(x_m)$ is the predicted target variable for
climate model $m$ and $M$ is the total number of climate models. The
uncertainty of the emergent relationship for a value $x$ that has not been used
to fit the regression line is given by the standard prediction error
$\sigma_{\hat{y}}(x)$:
\begin{equation}
  \sigma_{\hat{y}}^2(x) = s^2 \left[ 1 + \frac{1}{M} + \frac{\left( x - \bar{x}
    \right)^2}{\sum_{m=1}^M \left( x_m - \bar{x} \right)^2} \right].
  \label{eq:02:spe}
\end{equation}
Here, $\bar{x}$ indicates the arithmetic mean of $x$ over all climate models.
Assuming Gaussian errors and a mean of $\hat{y}(x)$ (\ie{} the best estimate of
the target variable $y$ is given by the regression line), \cref{eq:02:spe} can
be used to define a conditional \acf{PDF} for predicting a target variable of
$y$ given $x$:
\begin{equation}
  P(y|x) = \frac{1}{\sqrt{2 \pi \sigma_{\hat{y}}^2(x)}} \exp \left[
    -\frac{\left( y - \hat{y}(x) \right)^2}{2 \sigma_{\hat{y}}^2(x)} \right].
  \label{eq:02:pdf_y_given_x}
\end{equation}
This distribution describes the uncertainty in the emergent relationship itself
introduced by the imperfect alignment of the climate model data (red shaded
area in \cref{fig:02:emergent_constraint}). Its maximum is given by the
emergent relationship itself (red line in \cref{fig:02:emergent_constraint}).
The conditional \ac{PDF} can be interpreted as the posterior distribution of
the regression model based on the climate model output but constrained on the
observable $x$. However, the observed value of $x$, called $x_0$, also has
uncertainties associated with it (blue shaded are in
\cref{fig:02:emergent_constraint}). Assuming again a Gaussian distribution, the
observational \ac{PDF} for observing $x_0$ given the true value $x$ can be
written as
\begin{equation}
  P(x_0|x) = \frac{1}{\sqrt{2 \pi \sigma_x^2}} \exp \left[ -\frac{\left( x_0 -
    x \right)^2}{2 \sigma_x^2} \right],
  \label{eq:02:pdf_obs}
\end{equation}
where $\sigma_x$ is the standard deviation of the observation around the true
value. Assuming an imperfect uniform prior $P(x) \propto 1$ with cut-offs at
$-\infty$ and $+\infty$ and using Bayes' theorem implies $P(x_0|x) = P(x|x_0)$.
In a final step, this can be used to calculate the posterior \ac{PDF} for the
constrained prediction of the target variable $y$ given the observation $x_0$
(gray \ac{PDF} in \cref{fig:02:emergent_constraint}) with numerical
integration:
\begin{equation}
  P(y|x_0) = \int_{-\infty}^{+\infty} P(y|x) \, P(x|x_0) \dd{}x.
  \label{eq:02:pdf_y_given_x0}
\end{equation}
Posterior estimates of the target variable are influenced by the way the
statistical inference has been performed. Alternative methods that can be used
include Bayesian frameworks \autocite{Renoult2020}, information theoretic
approaches based on the Kullback–Leibler divergence between the models'
\acp{PDF} of $x$ and the observational \ac{PDF} \autocite{Brient2016} and
linear regression models based on hierarchical Bayesian models
\autocite{Nijsse2020}. However, no consensus has yet been found for this
statistical inference \autocite{Brient2020}.

One limitation of the presented approach is the assumption that the individual
data points from the different climate models are independent. As already noted
in the beginning of \cref{sec:02:reducing_uncertainties}, this is not the case
for typical climate models ensembles, as some modeling groups provide output
for multiple climate models and some climate models from different modeling
institutions share components and code \autocite{Knutti2013}. The duplicated
code in the different climate models leads to an overestimation of the sample
size and may result in spurious correlations \autocite{Sanderson2015}. Possible
approaches to tackle this problem are presented in
\cref{subsec:02:model_weighting} and include a weighting of the climate models
based on their degree of interdependence \autocite{Knutti2017a, Sanderson2015,
  Sanderson2017}. A further limitation of this approach is the use of an
ordinary least squares linear regression model. This is not always appropriate,
for example when a non-linear emergent relationship is expected
\autocite{Nijsse2020} or when additional physical considerations further
constrain the regression model, \eg{} by demanding a zero intercept ($a = 0$)
\autocite{Annan2020, JimenezdelaCuesta2019}. Moreover, using only a single
observational dataset to estimate $x_0$ and $\sigma_x$ when different datasets
are available might lead to an underestimation of the observational
uncertainty, as different observational datasets might lead to different
emergent constraints.

@@

In the last two decades, many emergent constraints on various aspects of the
Earth system have been published. Early studies tackled the hydrological cycle
\autocite{Allen2002} and the snow-albedo feedback \autocite{Hall2006}. Over the
years, the climate sensitivity expressed by the \ac{ECS} has been a prominent
target variable. Since cloud feedbacks are a major source of uncertainty for
climate sensitivity, a variety of papers focus on constraining \ac{ECS} with
cloud-related processes \autocite{Brient2015, Brient2016, Fasullo2012,
  Lipat2017, Sherwood2014, Su2014, Tian2015, Volodin2008, Qu2013, Zhai2015},
which are discussed in detail in
\cref{sec:05:comparison_of_emergent_constraints}. More recent studies aim to
constrain \ac{ECS} with the historical temperature variability
\autocite{Cox2018} or the historical warming trend
\autocite{JimenezdelaCuesta2019, Nijsse2020, Tokarska2020}. Emergent
constraints are not only limited to physical processes, but can also be applied
to other domains, like the global carbon cycle. For example, \textcite{Cox2013}
and \textcite{Wenzel2014} provide an emergent constraint on the terrestrial
climate-carbon feedback, \textcite{Wenzel2016} and \textcite{Winkler2019} on
the terrestrial concentration-carbon feedback. An extensive discussion on the
emergent constraint by \textcite{Wenzel2016} is given in \cref{sec:06:step_1}.
A further example of an emergent constraints on the carbon cycle focuses on
primary production in the tropical oceans \autocite{Kwiatkowski2017}.

@@

An alternative approach to emergent constraints are climate model weighting
schemes. Their basic idea is to abandon model democracy by replacing the
arithmetic mean used to calculate the \acp{MMM} by a weighted mean of the form
\begin{equation}
  y = \sum_{m=1}^{M} w_m y_m
  \label{eq:02:weighted_mean}
\end{equation}
with normalized weights $w_m$. Similar to the notation introduced in the
previous section, $y$ is a target variable (\eg{} a projection of the future
climate) and $m$ indexes the $M$ different climate models. To address two major
issues of model democracy (different climate models are not equally plausible
and not independent; see beginning of \cref{sec:02:reducing_uncertainties}),
\textcite{Knutti2017a} propose a weighting scheme based on climate model
performance and interdependence with the following weights:
\begin{equation}
  w_m \propto \frac{\exp \left( -\frac{D_m^2}{\sigma_D^2} \right)}{1 + \sum_{n
    \neq m}^{M} \exp \left( -\frac{S_{mn}^2}{\sigma_S^2} \right)}.
  \label{eq:02:knutti_weights}
\end{equation}
The metric $D_m$ describes the distance between climate model $m$ and
observations (= model performance) and the metric $S_{mn}$ describes the
distance between climate model $m$ and $n$ (= model interdependence).
$\sigma_D$ and $\sigma_S$ are constants that determine the individual strength
of the performance and interdependence weighting, respectively.

@@

Due to its flexibility, the climate model weighting scheme given by
\cref{eq:02:knutti_weights} has already been used for various target variables:
Arctic sea ice \autocite{Knutti2017a}, Antarctic ozone concentrations
\autocite{Amos2020}, North American maximum temperature \autocite{Lorenz2018},
European temperature and precipitation \autocite{Brunner2019, Merrifield2020}
and global warming over the \nth{21} century \autocite{Brunner2020,
  Liang2020a}.

@@

I do not like \ac{MDER}!

@@

- Difference to standard model weighting: weaker assumption (see Karpechko
2013)

>>>>

To quantify the effects of different feedbacks, a reference system with a basic
response needs to be defined, which is a crucial aspect of feedback analysis
\autocite{Roe2009}. Usually, the idealization of a blackbody Earth without an
atmosphere is used for that: In equilibrium, the incoming solar irradiance is
balanced with an outgoing thermal irradiance $J_0$ that solely depends on the
global mean surface temperature $T_0$ following the Stefan–Boltzmann law
\begin{equation}
  J_0 = -\sigma T_0^4.
  \label{eq:02:stefan_boltzmann_law_eq}
\end{equation}
$\sigma \approx 5.67 \unit{W m^{-2} K^{-4}}$ is the Stefan–Boltzmann constant.
To answer an external forcing $F$, the climate system reacts with a response
$R$ expressed by a change in the global mean surface temperature $\Delta T$:
\begin{equation}
  J_0 + R = -\sigma \left( T_0 + \Delta T \right)^4.
  \label{eq:02:stefan_boltzmann_law_non_eq}
\end{equation}
Since the temperature change caused by an anthropogenic forcing is much smaller
than the equilibrium temperature $\Delta T \ll T_0 \approx 255 \unit{K}$, a
simple first-order Taylor expansion can be used to linearize the blackbody
response:
\begin{equation}
  -\sigma \left( T_0 + \Delta T \right)^4 \approx J_0 - 4 \sigma T_0^3 \cdot
  \Delta T.
  \label{eq:02:stefan_boltzmann_law_lin}
\end{equation}
Thus, by comparing
\cref{eq:02:stefan_boltzmann_law_non_eq,eq:02:stefan_boltzmann_law_lin} the
climate response $R$ can be expressed as
\begin{equation}
  R = -4 \sigma T_0^3 \cdot \Delta T \coloneq \lambda_\text{BB} \cdot \Delta T
  \label{eq:02:linear_blackbody_response}
\end{equation}
with the blackbody feedback parameter $\lambda_\text{BB} \approx -3.8 \unit{W
  m^{-2} K^{-1}}$. Results from climate models and analyses of observations
confirm this linear relationship between $R$ and $\Delta T$
\autocite{Gregory2004}. However, the value of this linear constant $\lambda$,
the \emph{climate feedback parameter}, is found to be considerably larger than
the blackbody response ($\lambda \approx -1.0 \unit{W m^{-2} K^{-1}}$),
indicating that additional processes affect the Earth's radiative balance: the
climate feedbacks \autocite{Flato2013, Gregory2009}. Since climate models
suggest that the radiative effects of these additional feedbacks are also
proportional to $\Delta T$ \autocite{Gregory2008a},
\cref{eq:02:linear_blackbody_response} can be adjusted to
\begin{equation}
  R = \lambda \cdot \Delta T = \left( \lambda_\text{BB} + \lambda_\text{WV} +
  \lambda_\text{Albedo} + \lambda_\text{Cloud} + \dots \right) \cdot \Delta T.
  \label{eq:02:linear_response}
\end{equation}
$\lambda_\text{WV}$ refers to the water vapor feedback, $\lambda_\text{Albedo}$
to the snow/ice albedo feedback and $\lambda_\text{Cloud}$ to the cloud
feedback. Thus, the overall climate feedback parameter $\lambda$ can be written
as the sum of the individual feedback parameters $\lambda_i$:
\begin{equation}
  \lambda = \sum_i \lambda_i.
  \label{eq:02:lambda_as_sum_of_lambdas}
\end{equation}
Positive values of $\lambda_i$ indicate positive feedbacks (\eg{} the water
vapor feedback) and negative values indicate negative feedbacks (\eg{} the
blackbody feedback). This equation assumes that the individual radiative
responses from the different feedbacks are independent, which is a reasonable
first-order approximation but not entirely true \autocite{Soden2008}.

@@

One possible mathematical framework for the evaluation of emergent constraints
is based on linear regression and Gaussian probability densities
\autocite{Cox2013, Cox2018}. Let $x_m$ be the observable predictor variable for
climate model $m$ and $y_m$ the corresponding target variable. To find the
linear emergent relationship for the climate model ensemble $\left\{ \left(
x_m, y_m \right) \right\}$, a linear regression model
\begin{equation}
  \hat{y}(x) = b_0 + b_1 x
  \label{eq:02:linear_regression_y}
\end{equation}
for the predicted target variable $\hat{y}$ with intercept $b_0$ and slope
$b_1$ is used. Fitting this regression line with ordinary least squares
includes minimizing the standard error $s$ of the estimate
\begin{equation}
  s^2 = \frac{1}{M - 2} \sum_{m=1}^M \left( y_m - \hat{y}_m \right)^2,
  \label{eq:02:sse}
\end{equation}
where $\hat{y}_m \coloneq \hat{y}(x_m)$ is the predicted target variable for
climate model $m$ and $M$ is the total number of climate models. The
uncertainty of the emergent relationship for a value $x$ that has not been used
to fit the regression line is given by the standard prediction error
$\sigma_{\hat{y}}(x)$:
\begin{equation}
  \sigma_{\hat{y}}^2(x) = s^2 \left[ 1 + \frac{1}{M} + \frac{\left( x - \bar{x}
    \right)^2}{\sum_{m=1}^M \left( x_m - \bar{x} \right)^2} \right].
  \label{eq:02:spe}
\end{equation}
Here, $\bar{x}$ indicates the arithmetic mean of $x$ over all climate models.
Assuming Gaussian errors and a mean of $\hat{y}(x)$ (\ie{} the best estimate of
the target variable $y$ is given by the regression line), \cref{eq:02:spe} can
be used to define a conditional \acf{PDF} for predicting a target variable of
$y$ given $x$:
\begin{equation}
  P(y|x) = \frac{1}{\sqrt{2 \pi \sigma_{\hat{y}}^2(x)}} \exp \left[
    -\frac{\left( y - \hat{y}(x) \right)^2}{2 \sigma_{\hat{y}}^2(x)} \right].
  \label{eq:02:pdf_y_given_x}
\end{equation}
This distribution describes the uncertainty in the emergent relationship itself
introduced by the imperfect alignment of the climate model data (red shaded
area in \cref{fig:02:emergent_constraint}). Its maximum is given by the
emergent relationship itself (red line in \cref{fig:02:emergent_constraint}).
The conditional \ac{PDF} can be interpreted as the posterior distribution of
the regression model based on the climate model output but constrained on the
observable $x$. However, the observed value of $x$, called $x_0$, also has
uncertainties associated with it (blue shaded are in
\cref{fig:02:emergent_constraint}). Assuming again a Gaussian distribution, the
observational \ac{PDF} for observing $x_0$ given the true value $x$ can be
written as
\begin{equation}
  P(x_0|x) = \frac{1}{\sqrt{2 \pi \sigma_x^2}} \exp \left[ -\frac{\left( x_0 -
    x \right)^2}{2 \sigma_x^2} \right],
  \label{eq:02:pdf_obs}
\end{equation}
where $\sigma_x$ is the standard deviation of the observation around the true
value. Assuming an imperfect uniform prior $P(x) \propto 1$ with cut-offs at
$-\infty$ and $+\infty$ and using Bayes' theorem implies $P(x_0|x) = P(x|x_0)$.
In a final step, this can be used to calculate the posterior \ac{PDF} for the
constrained prediction of the target variable $y$ given the observation $x_0$
(gray \ac{PDF} in \cref{fig:02:emergent_constraint}) with numerical
integration:
\begin{equation}
  P(y|x_0) = \int_{-\infty}^{+\infty} P(y|x) \, P(x|x_0) \dd{}x.
  \label{eq:02:pdf_y_given_x0}
\end{equation}
Posterior estimates of the target variable are influenced by the way the
statistical inference has been performed. Alternative methods that can be used
include Bayesian frameworks \autocite{Renoult2020}, information theoretic
approaches based on the Kullback–Leibler divergence between the models'
\acp{PDF} of $x$ and the observational \ac{PDF} \autocite{Brient2016} and
linear regression models based on hierarchical Bayesian models
\autocite{Nijsse2020}. However, no consensus has yet been found for this
statistical inference \autocite{Brient2020}.

One limitation of the presented approach is the assumption that the individual
data points from the different climate models are independent. As already noted
in the beginning of \cref{sec:02:reducing_uncertainties}, this is not the case
for typical climate models ensembles, as some modeling groups provide output
for multiple climate models and some climate models from different modeling
institutions share components and code \autocite{Knutti2013}. The duplicated
code in the different climate models leads to an overestimation of the sample
size and may result in spurious correlations \autocite{Sanderson2015}. Possible
approaches to tackle this problem are presented in
\cref{subsec:02:model_weighting} and include a weighting of the climate models
based on their degree of interdependence \autocite{Knutti2017a, Sanderson2015,
  Sanderson2017}. A further limitation of this approach is the use of an
ordinary least squares linear regression model. This is not always appropriate,
for example when a non-linear emergent relationship is expected
\autocite{Nijsse2020} or when additional physical considerations further
constrain the regression model, \eg{} by demanding a zero intercept ($b_0 = 0$)
\autocite{Annan2020, JimenezdelaCuesta2019}. Moreover, using only a single
observational dataset to estimate $x_0$ and $\sigma_x$ when different datasets
are available might lead to an underestimation of the observational
uncertainty, as different observational datasets might lead to different
emergent constraints.

@@

In the last two decades, many emergent constraints on various aspects of the
Earth system have been published. Early studies tackled the hydrological cycle
\autocite{Allen2002} and the snow-albedo feedback \autocite{Hall2006}. Over the
years, the climate sensitivity expressed by the \ac{ECS} has been a prominent
target variable. Since cloud feedbacks are a major source of uncertainty for
climate sensitivity, a variety of papers focus on constraining \ac{ECS} with
cloud-related processes \autocite{Brient2015, Brient2016, Fasullo2012,
  Lipat2017, Sherwood2014, Su2014, Tian2015, Volodin2008, Qu2013, Zhai2015},
which are discussed in detail in
\cref{sec:05:comparison_of_emergent_constraints}. More recent studies aim to
constrain \ac{ECS} with the historical temperature variability
\autocite{Cox2018} or the historical warming trend
\autocite{JimenezdelaCuesta2019, Nijsse2020, Tokarska2020}. Emergent
constraints are not only limited to physical processes, but can also be applied
to other domains, like the global carbon cycle \autocite{Cox2013,
  Kwiatkowski2017, Wenzel2014, Wenzel2016, Winkler2019}. An extensive
discussion on the emergent constraint by \textcite{Wenzel2016}, which focuses
on the concentration-carbon feedback, is given in \cref{sec:06:step_1}.

@@

A further technique to reduce uncertainties in climate model projections with
observations are model weighting schemes. Their basic idea is to abandon model
democracy by replacing the arithmetic mean used to calculate the \acp{MMM} by a
weighted mean of the form
\begin{equation}
  y = \sum_{m=1}^{M} w_m y_m
  \label{eq:02:weighted_mean}
\end{equation}
with normalized weights $w_m$. Similar to the notation introduced in the
previous section, $y$ is a target variable (\eg{} a projection of the future
climate) and $m$ indexes the $M$ different climate models. To address two major
issues of model democracy (different climate models are not equally plausible
and not independent; see beginning of \cref{sec:02:reducing_uncertainties}),
\textcite{Knutti2017a} propose a weighting scheme based on climate model
performance and interdependence with the following weights:
\begin{equation}
  w_m \propto \frac{\exp \left( -\frac{D_m^2}{\sigma_D^2} \right)}{1 + \sum_{n
    \neq m}^{M} \exp \left( -\frac{S_{mn}^2}{\sigma_S^2} \right)}.
  \label{eq:02:knutti_weights}
\end{equation}
The metric $D_m$ describes the distance between climate model $m$ and
observations (= model performance) and the metric $S_{mn}$ describes the
distance between climate model $m$ and $n$ (= model interdependence).
$\sigma_D$ and $\sigma_S$ are constants that determine the individual strength
of the performance and interdependence weighting, respectively.

@@

The definition of the weights according to \cref{eq:02:knutti_weights} is based
on reasonable and comprehensible principles. However, the exact form of the
equation is purely subjective. Moreover, the additional freedom in choosing a
suitable metric and optimal values for the parameters $\sigma_D$ and $\sigma_S$
adds another level of subjectivity to the weighting scheme, which can partly be
addressed with the introduced leave-one-model-out \ac{CV} setup. Nevertheless,
due to its flexibility, the climate model weighting scheme of
\textcite{Knutti2017a} has already been used for various target variables:
Arctic sea ice \autocite{Knutti2017a}, Antarctic ozone concentrations
\autocite{Amos2020}, North American maximum temperature \autocite{Lorenz2018},
European temperature and precipitation \autocite{Brunner2019, Merrifield2020}
and global warming over the \nth{21} century \autocite{Brunner2020,
  Liang2020a}.

@@

An alternative approach to weighting climate models based on performance and
interdependence metrics is a technique called \emph{\ac{MDER}}. Similar to all
methods presented in \cref{sec:02:reducing_uncertainties}, it can be used to
reduce uncertainties in climate model projections with observations. The basis
of \ac{MDER} is a set of $K$ predictor diagnostics $\left\{ x^{(k)} \right\}$
with $k \in \left\{ 1, 2, \dots, K \right\}$ which are relevant for the
projection of the target variable $y$. The reasoning for this choice of the
diagnostics is similar to the one presented in the previous section: Weighting
schemes should address the question \enquote{which climate model is adequate
  for predicting the target variable?} and not \enquote{which climate model is
  the best?}.

The concept of \ac{MDER} is mathematically similar to the concept of emergent constraints. In a first step, an inter-model relationship between the target variable $y$ and the process-relevant diagnostics $\left\{ x^{(k)} \right\}$ is used to fit a multivariate linear regression model
\begin{equation}
  \bm{X}
\end{equation}

\begin{figure}[t]
  \centering
  \includegraphics[width=\FigureWidth{}]{
    ch02_scientific_background/figs/mder_schematic.pdf}
  \caption{Schematic illustration of the \acf{MDER} approach. First,
    inter-model relationships between a target variable $y$ and multiple
    process-based predictors $x^{(k)}$ (here: two predictors $x^{(1)}$ and
    $x^{(2)}$) are used to fit a multivariate linear regression model (gray
    plane). Second, observations of the predictors (horizontal thick black
    lines) are fed into the regression model to calculate climate models
    weights $w_m$ following \cref{eq:02:mder_weights}. The black circle
    indicates the best estimate for the target variable $y$ given by the
    observed values of $x^{(1)}$ and $x^{(2)}$. Each of the remaining colored
    circles represents a single climate model of the multi-model ensemble. The
    vertical dashed lines are auxiliary lines to visualize the distance
    between the climate model data and the linear regression surface.}
  \label{fig:02:mder}
\end{figure}

\begin{equation}
  w_m = xD
  \label{eq:02:mder_weights}
\end{equation}

@@

- Difference to standard model weighting: weaker assumption (see Karpechko
2013): The assumption that the regression between the present-day diagnostic
and a future-climatic variable— derived from climate models—holds also for true
cli- mate might seem to be weak at first sight, especially since it explicitly
requires imperfect models away from observed climate to span the desired
relationship. How- ever, a much weaker assumption is done in traditional
model-weighting approaches: a model that simulates present-day climate better
than another model neces- sarily better simulates future climate. Whereas
traditional approaches do not show this relationship, ensemble re- gression
establishes exactly such a relationship across a broad model ensemble.

- Techniques for diagnostic selection: hypothesis testing, forward iteration,
backwards elimination
